---
title: 'Analysis supplement: XXX Name of paper here.'
author: Ben Fosh, Ben Whalley
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---


This RMarkdown document documents the data cleaning and analysis of the P3CEQ reported in TODO ADDREFTOPAPER.


```{r}
set.seed(2018)
chpt <- checkpoint::checkpoint("2018-07-01")
library(eRm)
library(tidyverse)
library(pander)
knitr::opts_chunk$set(echo = T, message = F, warning = F, include = T, comment="", cache=T)
panderOptions("table.split.table", Inf)
```



# Import and clean data

```{r}
raw_data <- read.csv("DATAFILE.csv")

Q_selector <- raw_data %>%
  select(starts_with("Q")) %>%
  select(-Q9a, -Q12, -Q13, -Q14, -Q15, -Q16)

# Score adjustment for Each Q
A <- function(x) x - 1
rescore <- data.frame (cbind(apply(Q_selector[1:ncol(Q_selector)],2, A)))
rescore[rescore < 0] <- NA
rescore[rescore == 98] <- 0
rescore[rescore == 4] <- 3
rescore[rescore > 4] <- NA
rescore$Q05 <- (3 - rescore$Q05)

cleandata <- rescore
```


```{r}
qs <- cleandata
qs <- cleandata %>% 
  mutate(nmiss=rowSums(is.na(.))) %>% 
  # remove where only 1 item available
  filter(nmiss < (ncol(qs)-1)) %>% 
  select(-nmiss) 

write.csv(qs, "file path goes here")
```


# Partial credit models

Run the partial credit analysis:

```{r}
# select items
qs.no <- qs %>% select(Q01, Q02, Q03, Q05, Q06, Q07, Q08, Q09, Q10, Q11)
qs.no.clean <- qs.no %>% 
  mutate(nmiss=rowSums(is.na(.))) %>% 
  # remove where only 1 item available
  filter(nmiss < (ncol(qs.no)-1)) %>% 
  select(-nmiss) 

pcm.2 <- eRm::PCM(qs.no.clean)
```


ICC plots:

```{r}
plotICC(pcm.2, mplot = F, legpos = "right", ask = FALSE)
```


PI plots:

```{r}
pcm2.pp <- person.parameter(pcm.2)
plotPImap(pcm.2, sorted = TRUE, pp=pcm2.pp)
```


Item fit:

```{r}
pres.pcm <- person.parameter(pcm.2)
itemfit(pres.pcm)
itemfit
```


```{r}
thresholds(pcm.2)
```


Recreate the ICC plots, but also identify the cut/transition points in terms of probilities by summarising:

```{r}
itemfit(pcm2.pp)
pmat.df <- pmat(pcm2.pp) %>% as_data_frame()
pmat.df.sums <- pmat.df %>% 
  summarise_all(funs(mean(., na.rm=T))) %>% 
  reshape2::melt() %>%
  separate(variable, c("q", "item"))

pmat.df.sums %>% 
  reshape2::dcast(q~item) %>% 
  pander
```




Show where on the latent each question is adding information

```{r}
plotINFO(pcm.2, legpos = "right")
```


Plot PW map

```{r}
plotPWmap(pcm.2, imap=T)
```


Reliability parameters

```{r}
SepRel(pres.pcm)
```


