---
title: 'Analysis supplement: Validation of the P3CEQ.'
author: Ben Fosh, Ben Whalley
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---


# Setup

### Package requirements

We use the checkpoint library to snapshot package versions:

```{r}
# chpt <- checkpoint::checkpoint("2018-07-01")
library(eRm)
library(tidyverse)
library(pander)
```


### Setup and data processing

Import data:

```{r import}
# XXX BEN - note I have changed to use relative paths... this is best practice and makes it easier to replicate for others.
raw_data <- read_csv("rawdata.csv")
```


```{r clean}
# isolate items from data frame
items <- raw_data %>% select(Q1, Q2, Q3, Q4, Q5, Q6, Q7, Q8, Q8b, Q8c, Q8d, Q9, Q10, Q11)

# check data starts from 0
# XXX BEN YOU NEED TO EXPLAIN THIS CODE IN A COMMENT.. IT's weird-- why do this? Were some items recorded incorrectly? What 
for(i in 1:ncol(items)){
  if(0%in%items[,i]==FALSE){
    items[, i] = items[,i] - 1
}}
```




XXX WHAT about cases where you subtracted one from the column above... does this interact with the code below? Would seem to create an off-by-one for some columns?

```{r}
# Rescore response 99 (don't know) to 0
items[items >= 98] <- 0

# Rescore item 4 responses  to 3
items$Q4[items$Q4 >3] <- 3
```


Remove rows where only 1 item available:

```{r}
qs <- items %>% 
  filter(rowSums(is.na(.)) < (ncol(items)-1)) %>% 
  # take mean of Q8 items a different way - see below
  mutate(q8newALT = rowMeans(select(., Q8, Q8b, Q8c, Q8d), na.rm=T))
```

XXX Could do with a comment here explainign why these questions combined
XXX BEN -  I'm also concerned about this line unless it's deliberate:
```{r}
qs$q8new <- rowSums(qs[,c("Q8", "Q8b", "Q8c", "Q8d")], na.rm=TRUE) / 4
```

XXX The issue here is that you are summing then dividing by 4 to average, which effectively imputes a zero for the missing items. Is this what is wanted? the `q8newALT` variable above is the true mean of the available data, and this would create more missing values.

XXX See there is a real difference in computed score:

```{r}
round(qs$q8new, 0)-qs$q8newALT
```


Write out transformed data:

```{r}
write.csv(qs, "qs.csv")
```


# Partial Credit Models

Runs the Partial Credit Model:

```{r pcm, cache=T}
qs.no <- qs %>% select(Q1, Q2, Q3, Q5, Q6, Q9, Q10, Q11)
qs.no.clean <- qs.no %>% 
  mutate(nmiss=rowSums(is.na(.))) %>% 
  # remove where only 1 item available
  # XXX haven't you already done this above? Perhaps remove 2 lines below
  filter(nmiss < (ncol(qs.no)-1)) %>% 
  select(-nmiss) 

pcm.2 <- eRm::PCM(qs.no.clean)
```


ICC plots

```{r icc}
# get ICC plots
plotICC(pcm.2, mplot = F, legpos = "right", ask = FALSE)
```


PI Plots:

```{r PI}
pcm2.pp <- person.parameter(pcm.2)
plotPImap(pcm.2, sorted = TRUE, pp=pcm2.pp)
```


Model fit:

```{r fit}
pres.pcm <- person.parameter(pcm.2)
print(itemfit(pres.pcm), visible=F) %>% 
  broom::tidy() %>% 
  rename(Question=.rownames) %>% 
  pander()
```


Extract item thresholds:

```{r thresholds}
pcm2.thlds <- thresholds(pcm.2)
pcm2.thlds$threshtable[[1]] %>% broom::tidy() %>% 
    rename(Question=.rownames) %>% pander()
```


Summarise ICC plots with transition points:

```{r ICC_summarise}
pmat.df <- pmat(pcm2.pp) %>% 
  as_data_frame()

pmat.df %>% 
  summarise_all(funs(mean(., na.rm=T))) %>% 
  reshape2::melt() %>%
  separate(variable, c("q", "item")) %>% 
  reshape2::dcast(q~item) %>%
  rename(Question = q) %>% 
  setNames(names(.) %>% str_replace(., "c(\\d)", "Threshold \\1")) %>% 
  arrange(as.numeric(str_replace(Question, "Q", ""))) %>% 
  pander()
```


Identify where items add latent information:

```{r latent_plot }
plotINFO(pcm.2, legpos = "right")
```


Plot PW map:

```{r PWmap}
plotPWmap(pcm.2, imap=T)
```


Separation reliability:

```{r reliability}
SepRel(pres.pcm)
```



Note XXX to render simpler to just hit Shift Ctrk - K in RStudio... better than including this code here
